Bioverse: Origins of Life

### 2024-07-05 src/tex/ms.tex
add summary at the very end

\section{Conclusions and future work}

Our main findings are:
\begin{enumerate}
    \item Models of the Origins of Life provide hypotheses that are testable with near-future exoplanet surveys.
    \item The required \gls{NUV} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures that will be observationally testable.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets and the distribution of host star spectral types in the sample; in particular their past maximum \gls{NUV} fluxes.
%        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item If the predicted \gls{NUV} correlation exists, yielding strong evidence for it is likely ($> \SI{90}{\percent}$) for sample sizes $\geq 100$, and a survey strategy that targets extreme values of inferred past \gls{NUV} irradiation.
    \item Abiogenesis in the cyanosulfidic scenario prefers late host star spectral types due to the higher \gls{NUV} fluxes in their habitable zones. However, due to a wider distribution of maximum past \gls{NUV} fluxes in the \gls{HZ} of FGK stars, a transit survey targeting FGK systems is more likely to obtain strong evidence for or against the \gls{NUV} hypothesis.

@@

>>>>

\section{Conclusions and future work}
We have investigated the potential of upcoming exoplanet surveys to test the hypothesis that a minimum past \gls{NUV} flux is required for abiogenesis.
To this end, we first employed a semi-analytical Bayesian analysis to estimate probabilities of obtaining strong evidence for or against this hypothesis.
We then used the Bioverse framework to assess the diagnostic power of realistic transit surveys, taking into account exoplanet demographics, time-dependency of habitability and \gls{NUV} fluxes, observational biases, and target selection.

Our main findings are:
\begin{enumerate}
    \item The required \gls{NUV} radiation in the cyanosulfidic scenario should lead to a correlation between past \gls{NUV} flux and current occurrence of biosignatures that will be observationally testable.
    \item The required sample size for detecting this correlation depends on the occurrence of life on temperate exoplanets and the distribution of host star spectral types in the sample; in particular their past maximum \gls{NUV} fluxes.
%        A direct imaging mission with the \gls{HWO} will require characterizing XXX planets ...
    \item If the predicted \gls{NUV} correlation exists, yielding strong evidence for it is likely ($> \SI{90}{\percent}$) for sample sizes $\geq 100$, and a survey strategy that targets extreme values of inferred past \gls{NUV} irradiation.
    \item Abiogenesis in the cyanosulfidic scenario prefers late host star spectral types due to the higher \gls{NUV} fluxes in their habitable zones. However, due to a wider distribution of maximum past \gls{NUV} fluxes in the \gls{HZ} of FGK stars, a transit survey targeting FGK systems is more likely to obtain strong evidence for or against the \gls{NUV} hypothesis.

@@

Overall, our work demonstrates that upcoming exoplanet surveys have the potential to test the hypothesis that a minimum past \gls{NUV} flux is required for abiogenesis.
More generally, we found that models of the origins of life provide hypotheses that may be testable with near-future exoplanet surveys.
Our work highlights the importance of understanding the context in which a biosignature detection is made, which can not only help to assess the credibility of the detection but also to test competing theories of the origins of life on Earth and beyond.
